Bow shocks, bow waves, and dust waves

### 2019-01-14 papers/Papers1234/dusty-bow-wave.tex
Make a start on writing up the different dust regimes
Finish equations for different regimes in well-coupled case
Write more of inside-out section
Also, finish replacing the stellar data properly and re-doing the
figures for the new faster wind speeds.  And add Jane as an author,
since she has been helping with the stellar parameters.
Finish long footnote on stellar wind models
And add a bit to a new section about observations of IR arcs in Carina
Further simplification of the i-front trapping
Move the complicated version to an appendix, which will probably be
dropped from the final version
Ad

\usepackage{graphicx}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{fixltx2e}
\usepackage{booktabs}
\usepackage{siunitx}
\usepackage{color}
\usepackage{enumerate}
\usepackage{pdflscape}
\usepackage{rotating}
\usepackage{xr-hyper}
\usepackage{hyperref}
\externaldocument[Q-]{quadrics-bowshock}

@@

\title[Dust waves, bow waves, bow shocks]
{Shapes of dust waves, bow waves, and bow shocks}

\newcommand\AddressCRyA{Instituto de Radioastronom\'{\i}a y Astrof\'{\i}sica,
  Universidad Nacional Aut\'onoma de M\'exico, Apartado Postal 3-72,
  58090 Morelia, Michoac\'an, M\'exico}
\author[Henney \& Tarango Yong]{
  William J. Henney \& Jorge A. Tarango Yong\\
  \AddressCRyA
}

@@

\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle
\begin{abstract}
  Dust waves and bow waves result from the action of a star's
  radiation pressure on a stream of dust grains that is flowing past
  it.  They are an alternative mechanism to hydrodynamic bow shocks
  for explaining the curved arcs of infrared emission seen around some
  stars.  We employ simple cylindrically symmetric models for the dust
  grain dynamics under the influence of radiation and weak gas--grain
  coupling, which produce bow shapes that we call dragoids.  We also
  show how thin-shell hydrodynamic models can be modified to treat the
  case of strong gas-grain coupling, producing bow shapes that we call
  trapoids.  Using our recently developed two-dimensional
  classification scheme for projected bow shapes, we then analyze the
  inclination-dependent tracks of the dragoids and trapoids in the
  planitude--alatude plane, finding interesting differences from the
  wilkinoid, cantoid, and ancantoid shapes of hydrodynamic bow shock
  models. We further show how these are modified in the presence of
  small-amplitude standing-wave oscillations of the basic shape, as
  may be produced by hydrodynamic instabilities or a time-varying
  source.  We analyze the prospects of using shape analysis of
  observational datasets to discriminate between different bow models,
  finding that sample sizes of order 100 are required.
\end{abstract}

@@

\input{sec-dust-bow-intro}
\input{app-dust-wave}
\input{sec-standing-wave}
\input{sec-dust-bow-discuss}
\bibliographystyle{mnras}
\bibliography{bowshocks-biblio}
\appendix
\input{app-dust-equations}

>>>>

\usepackage{graphicx}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{fixltx2e}
\usepackage{booktabs}
\usepackage{siunitx}
\sisetup{separate-uncertainty = true}
\usepackage{color}
\usepackage{enumerate}
\usepackage{pdflscape}
\usepackage{rotating}
\usepackage{xr-hyper}
\usepackage{hyperref}
\externaldocument[Q-]{quadrics-bowshock}

@@

\title
{Bow shocks, bow waves, and dust waves}

\newcommand\AddressCRyA{Instituto de Radioastronom\'{\i}a y Astrof\'{\i}sica,
  Universidad Nacional Aut\'onoma de M\'exico, Apartado Postal 3-72,
  58090 Morelia, Michoac\'an, M\'exico}
\author[Henney, Arthur, \& Tarango Yong]{
  William J. Henney, S. Jane Arthur, \& Jorge A. Tarango-Yong\\
  \AddressCRyA
}

@@

\newcommand\Qp{\ensuremath{Q_{\text{p}}}}
\newcommand{\grain}{\ensuremath{_{\text{d}}}}
\newcommand{\B}{\ensuremath{_{\scriptscriptstyle\text{B}}}}
\newcommand{\alfven}{\ensuremath{_{\scriptscriptstyle\text{A}}}}
\newcommand{\xsec}{\ensuremath{\sigma\grain}}
\newcommand\frad{\ensuremath{f_{\text{rad}}}}
\newcommand\fmax{\ensuremath{f_{\text{max}}}}
\newcommand\thm{\ensuremath{\theta_{\text{m}}}}
\newcommand\drag{\ensuremath{_{\text{drag}}}}
\newcommand{\gas}{\ensuremath{_{\text{gas}}}}
\newcommand{\drift}{\ensuremath{_{\text{drift}}}}
\newcommand\rad{\ensuremath{_{\text{rad}}}}
\newcommand\Rmin{\ensuremath{R_{\scriptscriptstyle\text{min}}}}
% Why do I need both of these?
\newcommand\sound{\ensuremath{c_{\text{s}}}}
\newcommand\soundspeed{\ensuremath{c_{\text{s,gas}}}}
\newcommand\starstar{\ensuremath{_{**}}}

\defcitealias{Tarango-Yong:2018a}{Paper~I}
\newcommand\PaperI{\citetalias{Tarango-Yong:2018a}}

\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle
\begin{abstract}
  Dust waves and bow waves result from the action of a star's
  radiation pressure on a stream of dust grains that is flowing past
  it.  They are an alternative mechanism to hydrodynamic bow shocks
  for explaining the curved arcs of infrared emission seen around some
  stars.  We develop simple models for the combined effects of
  radiation and stellar winds on an ambient flow in the case where gas
  and grains are perfectly coupled. We find that wind-supported bow
  shocks predominate when the ambient density is low
  (\(\ltae \SIrange{100}{1000}{cm^{-3}}\)) for a broad class of
  stellar parameters.  At higher densities, radiation-supported bows
  can form, tending to be optically thin bow waves in the case of B
  stars, or optically thick bow shocks in the case of early O stars.
  We further investigate the dynamics of dust grains when the
  radiation field is sufficiently strong to overcome the collisional
  coupling between grains and gas, showing that this occurs at a
  \textit{rip-point}, where the ratio of radiation pressure to gas
  pressure exceeds a critical value (\(P\rad/\Pgas > 1000\)).

\end{abstract}

@@

\input{sec-dust-bow-intro}
\input{sec-dust-bow-discuss}
\bibliographystyle{mnras}
\bibliography{bowshocks-biblio}
\appendix
\input{app-cloudy-dust-charging}
\input{app-dust-wave}
\input{app-dust-equations}
%\input{app-dust-ifront-trap}
